\clearpage
\section{C++ Lambda Functions}

A lambda is a small function object defined where it is used. Its general form is

\mintinline{cpp}|auto name = [captures](parameters) -> return_type { body };|

\begin{description}
  \item[Capture list] \texttt{[captures]} selects automatic variables from the
    surrounding scope. An empty list captures nothing; captures may copy a value or
    refer to the original variable.
  \item[Parameters] \texttt{(parameters)} are the lambda's inputs, just like a
    function's parameters. The parentheses may be empty.
  \item[Return type] \texttt{-> return\_type} is optional. Usually the compiler
    infers it from the lambda's \texttt{return} statements.
  \item[Body] \texttt{\{ body \}} contains the statements run each time the lambda
    is called.
\end{description}

\subsection{Common Capture Modes}

Only variables actually used by a lambda are captured by the defaults
\texttt{[=]} and \texttt{[\&]}. Copies do not change the original variable;
references can change it and must not outlive it.

\begin{tabularx}{\textwidth}{@{}lX@{}}
  \texttt{[]} & Capture nothing. Surrounding local variables are unavailable. \\
  \texttt{[=]} & Copy each used surrounding variable. \\
  \texttt{[\&]} & Refer to each used surrounding variable. \\
  \texttt{[x]} & Copy only \texttt{x}. \\
  \texttt{[\&x]} & Refer only to \texttt{x}. \\
\end{tabularx}

\cppsnippet{snippets/cpp/lambda_captures.cpp}

\subsection{Sorting with a Lambda}

\texttt{std::sort(first, last, comparator)} calls the comparator with two elements.
It must return \texttt{true} exactly when the left element belongs before the right
one. For descending integers, that means \texttt{lhs > rhs}. Equal elements must
compare \texttt{false}; more generally, the comparator must define a strict weak
ordering. Sorting takes $O(n \log n)$ comparisons.

The captureless lambda and the named function below express the same ordering. The
lambda keeps a short, one-use rule beside the call and can capture local settings when
needed. The named function is easier to reuse, document, and test independently, but
it cannot directly capture local variables.

\cppsnippet{snippets/cpp/lambda_sort.cpp}
